---
title: "Your family's babynames"
author: "Your name"
output:
  pdf_document: default
  html_document: default
---

This document uses Hadley Wickham's R package `babynames`, which
contains 1.8 million name/year observations based on Social Security
data. Specifically, the data contains every name in the social
security records appearing  5 or more times in one year, and reports
the number of occurrences and the proportion for the year, by gender. For example, in 1920, about 0.8% of females had the name 'Irene'.

Note that the scale of the y axis differs across names. Also there are
close variants that I ignore (for example "Judy" vs "Judith").

\vspace{0.5in}

```{r plotnames, echo=FALSE, fig.width=3.75, fig.height=3.75, message=FALSE}
library(babynames); library(knitr); library(ggplot2); library(dplyr)

## put your family names here
namelist <- c('James', 'Mary')

for (i in namelist) {
  p = babynames %>% filter(name==i) %>%
    ggplot +
    geom_point(mapping=aes(x=year, y=prop, color=sex)) +
    labs(y='Proportion', x='Year') +
    ggtitle(paste('Popularity for', i)) + theme_bw() + 
    xlim(1880, 2014)
  print(p)
}
```


\newpage
The code, for those who might be interested:

```{r, ref.label='plotnames', eval=FALSE}
```

```{r namecount, echo=FALSE}
tmp = babynames %>% group_by(name, sex) %>% 
  summarize(Total=sum(n)) %>% arrange(-Total)
hd = head(tmp, n=10)
bt = tail(tmp, n=10)
```

One last thing: Here are the top 10 and bottom 10 names in the data, by the
number with that name (the bottom 10 are 
obviously alphabetical; there are 
`r format(sum(tmp$Total==5), big.mark=',')` names 
that occur in exactly one year, 5 times.)

```{r, echo=FALSE, results='asis'}
kable(hd, caption='Ten most common names' )
kable(bt, caption='Ten least common names')
```

